NEED TITLE

### 2014-11-11 ms.tex
improve density visualizations for 132
added more frames to folder, and to tex

\begin{figure*}
\plottwo{movie_disk_frame_0259.png}{Disk_0132_0000.png}
\plottwo{movie_disk_frame_0256.png}{movie_disk_frame_0272.png}
\caption{{\bf Change plots to show a zoom out for 132 and zoom in on the three regions that are the same} Slices along the angular momentum axis of four zoomed in simulation. To determine the angular momentum axis, we take a $0.01$ pc region about the densest local point and calculate the angular momentum vector. We then take a slice in the plane normal to the angular momentum to plot the regions around these dense points. \label{fig:snapshots}}
\end{figure*}

\begin{figure*}
\plottwo{movie_disk_frame_0259.png}{movie_disk_frame_0257.png}
\plottwo{movie_disk_frame_0256.png}{movie_disk_frame_0272.png}
\caption{{\bf Do same for other plots in 132} Slices along the angular momentum axis of four zoomed in simulation. To determine the angular momentum axis, we take a $0.01$ pc region about the densest local point and calculate the angular momentum vector. We then take a slice in the plane normal to the angular momentum to plot the regions around these dense points. \label{fig:snapshots 2}}
\end{figure*}

>>>>

\begin{figure*}
\plottwo{movie_disk_0132_0001.png}{movie_disk_0132_0003.png}
\plottwo{movie_disk_0132_0000.png}{Disk_0132_0000.png}
\caption{{\bf Change plots to show a zoom out for 132 and zoom in on the three regions that are the same} Slices along the angular momentum axis of four zoomed in simulation. To determine the angular momentum axis, we take a $0.01$ pc region about the densest local point and calculate the angular momentum vector. We then take a slice in the plane normal to the angular momentum to plot the regions around these dense points. \label{fig:snapshots}}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.48\textwidth]{movie_disk_0132_0002.png}
\includegraphics[width=0.48\textwidth]{movie_disk_0132_0004.png}
\centering{\includegraphics[width=0.48\textwidth]{Disk_0132_0002.png}}
\caption{{\bf Do same for other plots in 132} Slices along the angular momentum axis of four zoomed in simulation. To determine the angular momentum axis, we take a $0.01$ pc region about the densest local point and calculate the angular momentum vector. We then take a slice in the plane normal to the angular momentum to plot the regions around these dense points. \label{fig:snapshots 2}}
\end{figure*}

\begin{figure*}
\plottwo{Track_0132_000_rho.png}{pdf_frame_0132_0000.png}
\plottwo{Track_0132_000_vr.png}{Track_0132_000_mass.png}
\caption{Tracking plot for density and associated pdf graphs for two regions.  The density graphs have slopes of -3/2, -2, and -5/2 shown for reference.  The upper density frame on the left shows a consistent slope matching the -3/2 reference line very nicely.  The pdf graphs show three volumes, one at 1pc, one at 2pc, and one at 5pc.  \label{fig:Track_and_pdf_000}}
\end{figure*}

\begin{figure*}
\plottwo{Track_0132_002_rho.png}{pdf_frame_0132_0002.png}
\plottwo{Track_0132_002_vr.png} {Track_0132_002_mass.png}
\caption{Tracking plot for density and associated pdf graphs for two regions.  The density graphs have slopes of -3/2, -2, and -5/2 shown for reference.  The upper density frame on the left shows a consistent slope matching the -3/2 reference line very nicely.  The pdf graphs show three volumes, one at 1pc, one at 2pc, and one at 5pc.  \label{fig:Track_and_pdf_002}}
\end{figure*}
